PIC simulation of instabilities in relativistic supernovae shocks

### 2021-04-09 papers/Physica2021/Romansky_Physica2021.tex

\begin{document}
	\title{Evaluating MHD parameters of relativistic shock waves with particle-in-cell modeling}

@@

	\begin{abstract}
                 Relativistic plasma outflows are observed in gamma-ray burst 
		sources, jets of active galactic nuclei, pulsar wind nebulae and
		supernovae explosions. Magnetohydrodynamical (MHD) shock waves
		inevitably result from interactions of such relativistic outflows with
		the ambient interstellar matter. The widely used single-fluid MHD
		description of relativistic shock waves is the main tool to study the
		global structure of such objects. However, to justify the validity of 
		the global MHD models and to interpret the observed
		emission spectra of space objects with relativistic shocks, a kinetic
		description of electrons, positrons, and ions at microscales is needed. 
		We model a plane relativistic shock propagating  transverse to a regular magnetic field in the electron-ion plasmas with imposed turbulent fluctuations in the shock upstream.   
           Namely we study  the effect of the micro-scale plasma processes on 
		macroscopic parameters of the mildly-relativistic shocks as the adiabatic index
		of the relativistic fluid in the shock downstream. The adiabatic index is a macroscopic parameter of the
		single-fluid MHD models commonly used for shock modeling at much
		longer hydrodynamical scales and it is especially important for the MHD modeling of the mildly-relativistic shocks.
	\end{abstract}

>>>>

\begin{document}
	\title{PIC simulation of instabilities in relativistic supernovae shocks}

@@

	\begin{abstract}
                 Modern observations show presence of relativistic supernovae - objects intermediate between regular supernovae and gamma-ray bursts. The typical lorentz-factors of plasma flows in relativistic supernovae are about $1.5$. The process of cosmic ray acceleration is very different from both non-relativistic and ultra-relativistic case. In this paper is presented particle-in-cell modeling of trans-relativistic collisionless shocks. It is shown, that development of magneto-hydrodynamic instabilities, particularly Bell's instability, has strong influence on cosmic ray acceleration. At times larger than $1500$ reverse ion plasma frequency magnetic field, generated by Bell's instability, significantly suppresses the electrons' spectrum. This effect should be taken into account for modeling of synchrothron spectrum from relativistic supernovae.
	\end{abstract}
